---
title: "Case Study Report"
date: "`r Sys.Date()`"
author: "Your Name"
institute: "Numeric Mind"
output:
  html_document
    #toc: yes
    #toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set()
```

Covid-19 Nepal 

Abstract

This report was made with the help of Numeric Mind - Data Analysis with R training. Here, we have last 7 days daily count of Covid-19 confirmed cases in Nepal. This report has been generated by R Markdown.

Data 

We collected data from John Hopkins University - GitHub Repo.
And filtered data of Nepal to generate following table.

```{r}
library(kableExtra)

readRDS("last_7_days.rds") %>% 
  head() %>% 
  kbl(caption = "Table 1: Nepal Covid-19 Daily Data") %>%
  kable_classic(full_width = F,  html_font = "Cambria", position = "center", font_size = 15) #%>% 
  #column_spec(1:4, width = "10em")
```

## Figures

We plotted above data in a barplot using ggplot2.


### Last 7 Days Plot

```{r}

# readRDS("plot_4.rds")

```
### Comparison Plot

```{r}
# readRDS("comp_plot.rds") 
```

### Age Group vs Sex Plot

```{r}
# readRDS("age_grp.rds")
```

### Province vs Sex

```{r}
# readRDS("province_sex.rds")
```


